---
title: "Get on your soapbox!"
subtitle: "Blog content and promotion"
author: "Maëlle Salmon (`r icon::fa('twitter')` ma_salmon, `r icon::fa('github')` maelle)"
date: "2018/03/15"
output:
  xaringan::moon_reader:
    css: ["default", "rladies", "rladies-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(echo = TRUE, cache = TRUE,
                      fig.align = 'center',
                      fig.width = 15, message = FALSE)
```

# My place in the R community

```{r}
library("magrittr"); library("magick")
row1 <- c(image_read("locke.png"), image_read("rweekly.png")) %>% image_append()
row2 <- c(image_read("ropensci.png"), image_read("rladies.png")) %>% image_append()

image_blank(225, 200, col = "white") %>%
  image_composite(row1, offset = "+0+100") %>%
  image_composite(row2, offset = "+50+25") 
```

---

# What can you blog about?

Things you enjoy!

Just started learning. Edwin's blog post.

---

# How to get stuff done?

Don't let stress spoil the _fun_.

Do not get too ambitious

Kasia's strategy https://kkulma.github.io/2017-12-29-end-of-year-thoughts/

🚢 it!

---

# Store your ideas

* Your usual note taking workflow: notebook, fancy app (Trello?), etc.

* I have a notebook and used to have an empty GitHub repo with ideas as issues.

---

# Store your ideas Suzan Baert's cupboard


```{r, echo = FALSE}
image_read("assets/suzan_cupboard.jpg")
```

http://suzan.rbind.io/

---


https://www.johnmackintosh.com/2017-12-30-time-to-shine/

https://vgpena.github.io/good-is-better-than-perfect/

https://ozar.me/2015/04/is-your-blog-cheers-or-mcdonalds/

https://maraaverick.rbind.io/2017/10/keeping-up-with-blogdown/

---

# Thank you!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan) by Yihui Xie with the R-Ladies theme by Alison Presmanes Hill. 💜


---