---
title: "Get on your soapbox!"
subtitle: "Blog content and promotion"
author: "Maëlle Salmon (`r icon::fa('twitter')` ma_salmon, `r icon::fa('github')` maelle)"
date: "2018/03/15"
output:
  xaringan::moon_reader:
    css: ["default", "rladies", "rladies-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(echo = TRUE, cache = TRUE,
                      fig.align = 'center',
                      fig.width = 15, message = FALSE)
```

# My place in the R community

```{r}
library("magrittr"); library("magick")
row1 <- c(image_read("locke.png"), image_read("rweekly.png")) %>% image_append()
row2 <- c(image_read("ropensci.png"), image_read("rladies.png")) %>% image_append()

image_blank(225, 200, col = "white") %>%
  image_composite(row1, offset = "+0+100") %>%
  image_composite(row2, offset = "+50+25") 
```

---

# What can you blog about?

Things you enjoy! 



---

# What can you blog about?

Things you've just learnt. Edwin Thoen's https://edwinth.github.io/blog-new-things/ says

* _It forces you to study deeply_

* _You understand other learners_

* _You draw attention of experts_

* _You train in being wrong_


---

# Explore your idea

* Google it! 

* If you find similar work, link it in your post.


---

# About links

Other blog posts, Package docs, anything really.

```{r}
rtweet::tweet_shot("950476076215558144")

```


---

# Find your own voice

* I'm no writing coach but I'd say, be sincere.

* What language? English or your own? Or two of them like Daniela Vasquez https://d4tagirl.com/

---

# How to get stuff done?

Don't let stress and perfectionism spoil the _fun_.

Do not get too ambitious

🚢 it!

Kasia's strategy: https://kkulma.github.io/2017-12-29-end-of-year-thoughts/

---

# Store your ideas

* Your usual note taking workflow: notebook, fancy app (Trello?), etc.

* I have a notebook and used to have an empty GitHub repo with ideas as issues.

---

# Store your ideas: Suzan Baert's cupboard


```{r, echo = FALSE}
image_read("assets/suzan_cupboard.jpg")
```

http://suzan.rbind.io/

---


https://www.johnmackintosh.com/2017-12-30-time-to-shine/

https://vgpena.github.io/good-is-better-than-perfect/

https://ozar.me/2015/04/is-your-blog-cheers-or-mcdonalds/

https://maraaverick.rbind.io/2017/10/keeping-up-with-blogdown/

---

# Thank you!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan) by Yihui Xie with the R-Ladies theme by Alison Presmanes Hill. 💜


---