---
title: "Get on your soapbox!"
subtitle: "Blog content and promotion"
author: "Maëlle Salmon. R-Ladies Global social master <br/> `r icon::fa('twitter')` ma_salmon, `r icon::fa('github')` maelle"
date: "2018/03/15"
output:
  xaringan::moon_reader:
    css: ["default", "rladies", "rladies-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(echo = TRUE, cache = TRUE,
                      fig.align = 'center',
                      fig.width = 15, message = FALSE)
```

# My place in the R community

```{r}
library("magrittr"); library("magick")
row1 <- c(image_read("locke.png"), image_read("rweekly.png")) %>% image_append()
row2 <- c(image_read("ropensci.png"), image_read("rladies.png")) %>% image_append()

image_blank(225, 200, col = "white") %>%
  image_composite(row1, offset = "+0+100") %>%
  image_composite(row2, offset = "+50+25") 
```

---



# My blogging journey

I don't use blogdown yet!

http://www.masalmon.eu/

<iframe src="https://giphy.com/embed/76C4f4bfzbQqI" width="480" height="270" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/work-share-hard-76C4f4bfzbQqI">via GIPHY</a></p>

---

# What can you blog about?

* Your latest R obsession? Me in http://www.masalmon.eu/2018/02/22/hexcombine/

--

* Something you've just implemented? Omayma Said http://omaymas.github.io/prophet_explore/

--

* Something _you_ like! Kasia Kulma https://kkulma.github.io/2017-12-16-star-wars-vs-star-trek-word-battle/

--

* Fun packages?  Mine Çetinkaya-Rundel's list  http://www2.stat.duke.edu/courses/Fall17/sta112.01/assignment/08-mini-hw.html

---

# What can you blog about?

Things you've just learnt. Edwin Thoen's https://edwinth.github.io/blog-new-things/ says

* _It forces you to study deeply_

* _You understand other learners_

* _You draw attention of experts_

* _You train in being wrong_


---

# What can you blog about?

Not necessarily R code!

--

* A list of things that helped you learn Lorna Maria Aine in https://medium.com/@lornamariak/r-libraries-to-aid-you-learn-data-science-in-2018-30eaaf7cc050

--

* Your experience at an event e.g. Jasmine Dumas in https://jasdumas.github.io/2017-05-28-runconf17-experience/

--

* Your experience at work e.g. Julia Silge in https://juliasilge.com/blog/one-year-at-stack/


---

# Find inspiration

Read other blogs! 

* R Weekly newsletter https://rweekly.org/

* \#rstats on Twitter https://twitter.com/search?q=%23rstats&src=savs

<iframe src="https://giphy.com/embed/34ZNcoaN5u4hi" width="480" height="360" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/reading-bored-wallace-and-gromit-34ZNcoaN5u4hi">via GIPHY</a></p>

---

# Explore your idea

* Google it! 

* If you find similar work, link it in your post.

<iframe src="https://giphy.com/embed/10UeedrT5MIfPG" width="480" height="350" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/dancing-happy-cartoons-10UeedrT5MIfPG">via GIPHY</a></p>

---

# About links

Other blog posts, Package docs, anything really.

<blockquote class="twitter-tweet" data-lang="ca"><p lang="en" dir="ltr">My favorite thing to do when writing any blog post is linking the heck out of everything because I want every post to be a multi-directional springboard for curious people.</p>&mdash; Mikhail Popov (@bearloga) <a href="https://twitter.com/bearloga/status/950476076215558144?ref_src=twsrc%5Etfw">8 de gener de 2018</a></blockquote>


---

# Find your own voice

* I'm no writing coach but I'd say, be sincere.

* What language? English or your own? Or both like Daniela Vázquez https://d4tagirl.com/

<iframe src="https://giphy.com/embed/3o6ozsCihBgPhJz52o" width="480" height="271" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/angrybirds-angry-birds-movie-angrybirdsmovie-3o6ozsCihBgPhJz52o">via GIPHY</a></p>

---

# How to get stuff done?

Proofread and do your best but...

Don't let stress and perfectionism spoil the _fun_.

Do not get too ambitious

🚢 it!

Kasia Kulma's strategy: https://kkulma.github.io/2017-12-29-end-of-year-thoughts/

---

# Store your ideas

* Your usual note taking workflow: notebook, fancy app (Trello?), etc.

* I have a notebook and used to have an empty GitHub repo with ideas as issues.

<iframe src="https://giphy.com/embed/cur2pARDPMbEk" width="480" height="270" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/cur2pARDPMbEk">via GIPHY</a></p>

---

# Store your ideas: Suzan Baert's cupboard


```{r, echo = FALSE}
image_read("assets/suzan_cupboard.jpg")
```

http://suzan.rbind.io/

---

# My recipe to tweet a blog post

* Title and link!

* \#rstats and other hashtag if needed

* A figure or a gif!

* Emojis!

* Tag package authors? Listen to their feed first

---

# My recipe to tweet a blog post

```{r}

rtweet::tweet_shot("966799442430054400")%>%
  magick::image_crop("517x300+0+90")
```

---
# Add your blog to lists!

* https://github.com/sellorm/awesome-blogdown

* https://support.rbind.io/about/


---

# Promote your blog: RSS feed

Create its RSS feed

* Submit it to https://rweekly.org/submit (RSS feed or individual links!)

* Submit it to R Bloggers? https://www.r-bloggers.com/add-your-blog/

<iframe src="https://giphy.com/embed/26hitupaLP1ekljJS" width="480" height="360" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/love-animation-happy-26hitupaLP1ekljJS">via GIPHY</a></p>

---

# Take advantage of R-Ladies networks

* Ping your local chapter

* Ping me/R-Ladies Global Twitter account! https://twitter.com/rladiesglobal

---

# The particular case of rOpenSci

If you use one of https://ropensci.org/packages/

Tell us (`r icon::fa('twitter')`` rOpenSci https://ropensci.org/contact/) and the link will be added to rOpenSci newsletter! https://ropensci.github.io/biweekly/


---

# Don't miss this offer!

<blockquote class="twitter-tweet" data-lang="ca"><p lang="en" dir="ltr">&quot;if you’re early in your career as a data scientist and you start a data-related blog, tweet me a link at <a href="https://twitter.com/drob?ref_src=twsrc%5Etfw">@drob</a> and I’ll tweet about your first post&quot; 👌☄ <a href="https://t.co/FaXrgVcE0P">https://t.co/FaXrgVcE0P</a></p>&mdash; R-Ladies Global (@RLadiesGlobal) <a href="https://twitter.com/RLadiesGlobal/status/930494182027923457?ref_src=twsrc%5Etfw">14 de novembre de 2017</a></blockquote>


---

# Be the blog reader you want to see

* Leave comments: compliments, questions, suggestions, corrections

* Share links with your network!

* Link it back on your blog


---



# Thank you!

https://github.com/maelle/rladiesct

http://www.masalmon.eu/rladiesct/slides

<iframe src="https://giphy.com/embed/l4KibK3JwaVo0CjDO" width="240" height="237" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/afv-funny-fail-lol-l4KibK3JwaVo0CjDO">via GIPHY</a></p>

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan) by Yihui Xie with the R-Ladies theme by Alison Presmanes Hill. 💜


---