---
title: "Get on your soapbox!"
subtitle: "Blog content and promotion"
author: "Maëlle Salmon (`r icon::fa('twitter')` ma_salmon, `r icon::fa('github')` maelle)"
date: "2018/03/15"
output:
  xaringan::moon_reader:
    css: ["default", "rladies", "rladies-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(echo = TRUE, cache = TRUE,
                      fig.align = 'center',
                      fig.width = 15, message = FALSE)
```

# My place in the R community

```{r}
library("magrittr"); library("magick")
row1 <- c(image_read("locke.png"), image_read("rweekly.png")) %>% image_append()
row2 <- c(image_read("ropensci.png"), image_read("rladies.png")) %>% image_append()

image_blank(225, 200, col = "white") %>%
  image_composite(row1, offset = "+0+100") %>%
  image_composite(row2, offset = "+50+25") 
```

---



# My blogging journey

I don't use blogdown yet!

http://www.masalmon.eu/

I am having a lot of fun!

---

# What can you blog about?

* Your latest R obsession? Me in http://www.masalmon.eu/2018/02/22/hexcombine/

--

* Something _you_ like! Kasia Kulma https://kkulma.github.io/2017-12-16-star-wars-vs-star-trek-word-battle/

--

* Fun packages?  Mine Çetinkaya-Rundel's list  http://www2.stat.duke.edu/courses/Fall17/sta112.01/assignment/08-mini-hw.html

---

# What can you blog about?

Things you've just learnt. Edwin Thoen's https://edwinth.github.io/blog-new-things/ says

* _It forces you to study deeply_

* _You understand other learners_

* _You draw attention of experts_

* _You train in being wrong_


---

# What can you blog about?

Not necessarily R code!

* A list of things that helped you learn Lorna Maria Aine in https://medium.com/@lornamariak/r-libraries-to-aid-you-learn-data-science-in-2018-30eaaf7cc050

--

* Your experience at an event e.g. Jasmine Dumas in https://jasdumas.github.io/2017-05-28-runconf17-experience/

--

* Your experience at work e.g. Julia Silge in https://juliasilge.com/blog/one-year-at-stack/


---

# Find inspiration

Read other blogs! 

* R Weekly newsletter

* \#rstats on Twitter


---

# Explore your idea

* Google it! 

* If you find similar work, link it in your post.


---

# About links

Other blog posts, Package docs, anything really.

```{r}
rtweet::tweet_shot("950476076215558144")

```


---

# Find your own voice

* I'm no writing coach but I'd say, be sincere.

* What language? English or your own? Or two of them like Daniela Vasquez https://d4tagirl.com/

---

# How to get stuff done?

Don't let stress and perfectionism spoil the _fun_.

Do not get too ambitious

🚢 it!

Kasia's strategy: https://kkulma.github.io/2017-12-29-end-of-year-thoughts/

---

# Store your ideas

* Your usual note taking workflow: notebook, fancy app (Trello?), etc.

* I have a notebook and used to have an empty GitHub repo with ideas as issues.

---

# Store your ideas: Suzan Baert's cupboard


```{r, echo = FALSE}
image_read("assets/suzan_cupboard.jpg")
```

http://suzan.rbind.io/

---

# My recipe to tweet a blog post

* Title and link!

* #\rstats and other hashtag if needed

* A figure or a gif!

* Emojis!

* Tag package authors? Listen to their feed first

---

# My recipe to tweet a blog post

```{r}

rtweet::tweet_shot("966799442430054400")
```

---
# Add your blog to lists!

* https://github.com/sellorm/awesome-blogdown

* https://support.rbind.io/about/


---

# Promote your blog: RSS feed

Create its RSS feed

* Submit it to https://rweekly.org/submit (RSS feed or individual links!)

* Submit it to R Bloggers? https://www.r-bloggers.com/add-your-blog/

---

# Take advantage of R-Ladies network

* Ping your local chapter

* Ping me/R-Ladies Global Twitter account!

---

#  The particular case of rOpenSci

If you use one of https://ropensci.org/packages/

Tell us and the link will be added to rOpenSci newsletter!


---

#Don't miss this offer!

```{r}
rtweet::tweet_shot("930494182027923457")

```

---

# Be the blog reader you want to see

* Leave comments: compliments, questions, suggestions, corrections

* Share links with your network!

* Link it back on your blog


---



# Thank you!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan) by Yihui Xie with the R-Ladies theme by Alison Presmanes Hill. 💜


---